---
title: "Individual1"
author: "Evan Mills"
date: "April 17, 2019"
output: html_document
---

```{r}
library(ggplot2)
library(dplyr)

acc <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/fars2017/accident.csv", stringsAsFactors = FALSE)
```

```{r}
pers <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/fars2017/person.csv", stringsAsFactors = FALSE)
```

Part One: Acciednt Data
```{r}
ggplot(data = acc, aes(x = DAY_WEEK)) + geom_bar()
```

As you can see by the chart above accidents tend to happen on what we consider the weekend. That is days 6, 7, and 8 in the chart above.

```{r}
ggplot(data = acc, aes(x = HOUR), colour = HOUR) + geom_bar() + xlim(c(-1,25))
```

As you can see from the chat above the greatest number of accidents happens at hour 18 which equates to 6:00 pm. However the time period that accounts for most of the accidents is hour 14 to hour 22, which in non-24 hour time is 2:00 pm to 10:00 pm. This corrlates with the time period know as rush hour.
```{r}
dui <- acc %>% select(DRUNK_DR) %>% filter(DRUNK_DR >= 1)

dim(dui)

unique(acc$YEAR)
```

There were 8769 accidents that involved at least one drunk driver in 2017. 